---
title: "Income Outcomes"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(flexdashboard)
library(plotly)
library(tidyverse)
```

Row {.tabset}
-----------------------------------------------------------------------

### Income at Age 35

```{r,echo=FALSE, out.width="100%", message=FALSE, warning=FALSE}
load("./plots/overall.Rdata")
overall_trend
```

### Income by Race 

```{r,echo=FALSE, out.width="100%", message=FALSE, warning=FALSE}
load("./plots/outcomes_race.Rdata")
outcomes_race
```

### Income by Parents' Income 

```{r,echo=FALSE, out.width="100%", message=FALSE, warning=FALSE}
load("./plots/outcomes_parents.Rdata")
outcomes_parents
```

Row 
-----------------------------------------------------------------------
 

### Number of Children By Percent of Tract Above Poverty Level {data-width=500}

```{r}
ggplotly(ggplot()+geom_histogram(aes(x=rnorm(100))))
```


### Notes {data-width=250}

This analysis uses data from OpportunityInsights.org. 

* The data set links children who were graduating high school before the 2000 US Census to the tract they grew up in and their income at age 35. 
* Data on the federal poverty level reflects overall rate in the tract when these children were school-aged, not the poverty status of the children themselves.
* Explore this data at www.opportunityatlas.org




