---
title: "Opportunity Index"
output: 
  flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(crosstalk)
library(sf)
library(leaflet)
library(plotly)
library(DT)
library(tidyverse)

load("./data for markdowns/opp_ind_sf.Rdata")
# load("./data for markdowns/resources.Rdata")

sd <- SharedData$new(as_Spatial(opp_ind_sf))
sd_df <- SharedData$new(
  as.data.frame(as_Spatial(opp_ind_sf)@data),group = sd$groupName())
bins <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
pal <- colorBin("RdYlBu", domain = sd$r_COI_met, bins = bins)

```



Child Opportunity Index
=======================================================================

<!-- Inputs {.sidebar} -->
<!-- ----------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- filter_slider( -->
<!--   id = "pct_child_under_fpl",  -->
<!--   label = "Percent of Children in Poverty",  -->
<!--   sharedData = sd_df, -->
<!--   column = ~pct_child_under_fpl) -->

<!-- filter_slider( -->
<!--   "pct_nonwhite",  -->
<!--   "Percent of Children who are Non-white",  -->
<!--   sharedData = sd_df, -->
<!--   column = ~pct_nonwhite) -->

<!-- filter_slider( -->
<!--   "pct_under_18",  -->
<!--   "Percent of Population Under 18",  -->
<!--   sharedData = sd_df,  -->
<!--   column = ~pct_under_18) -->
<!-- ``` -->

<!-- --- -->

Column {data-width=600}
-----------------------------------------------------------------------

### {}

```{r}

bins <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)
pal <- colorBin("RdYlBu", domain = sd$r_COI_met, bins = bins)
pal_ed <- colorBin("RdYlBu", domain = sd$r_ED_met, bins = bins)
pal_se <- colorBin("PiYG", domain = sd$r_SE_met, bins = bins)
pal_he <- colorBin("BrBG", domain = sd$r_HE_met, bins = bins)
pal_coi <- colorBin("RdBu", domain = sd$r_COI_met, bins = bins)

labels_COI <- sprintf(
  "<img src = 'https://github.com/npiepgrass/community-dashboards/blob/main/markdowns/plots/mapminis/%s.png?raw=true' width = 300><br/><strong>%s</strong><br/>%s, %s County<br/><strong>Child Opportunity: %g/100</strong>",
  opp_ind_sf$geoid,opp_ind_sf$subneighbor, opp_ind_sf$neighbor, opp_ind_sf$county, opp_ind_sf$r_COI_met
) %>% lapply(htmltools::HTML)
labels_ED <- sprintf(
  "<strong>%s</strong><br/>%s, %s County<br/><strong>Education: %g/100</strong>",
  opp_ind_sf$subneighbor, opp_ind_sf$neighbor, opp_ind_sf$county, opp_ind_sf$r_ED_met
) %>% lapply(htmltools::HTML)
labels_SE <- sprintf(
  "<strong>%s</strong><br/>%s, %s County<br/><strong>Social and Economic: %g/100</strong>",
  opp_ind_sf$subneighbor, opp_ind_sf$neighbor, opp_ind_sf$county, opp_ind_sf$r_SE_met
) %>% lapply(htmltools::HTML)
labels_HE <- sprintf(
  "<strong>%s</strong><br/>%s, %s County<br/><strong>Health and Environment: %g/100</strong>",
  opp_ind_sf$subneighbor, opp_ind_sf$neighbor, opp_ind_sf$county, opp_ind_sf$r_HE_met
) %>% lapply(htmltools::HTML)


leaflet() %>% 
  addTiles(group = "Basemap") %>%
  addPolygons(data=sd,
              color = NA, 
              fillColor = ~pal(r_COI_met), 
              fillOpacity = .7,
              group = "Opportunity Index (Overall)",
              label = labels_COI,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto")) %>% 
  addPolygons(data=sd,
              color = NA,
              fillColor = ~pal(r_ED_met),
              fillOpacity = .7,
              group = "Education Index",
              label = labels_ED,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto")) %>%
  addPolygons(data=sd,
              color = NA,
              fillColor = ~pal(r_SE_met),
              fillOpacity = .7,
              group = "Social and Economic Index",
              label = labels_SE,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto")) %>%
  addPolygons(data=sd,
              color = NA,
              fillColor = ~pal(r_HE_met),
              fillOpacity = .7,
              group = "Health and Environment Index",
              label = labels_HE,
              labelOptions = labelOptions(
                style = list("font-weight" = "normal", padding = "3px 8px"),
                textsize = "13px",
                direction = "auto")) %>%
  addPolygons(data=sd,
              color = "black", 
              fill = NA, 
              weight = 1,
              opacity = 1,
              group = "Neighborhood Outlines") %>% 
  addPolygons(data=sd,
              color = "black", 
              fill = NA, 
              weight = 2.5,
              opacity = 1,
              group = "County Outlines") %>% 
  addLayersControl(
    baseGroups = c("Opportunity Index (Overall)","Education Index",
                   "Social and Economic Index", "Health and Environment Index"),
    overlayGroups = c("Basemap", "Neighborhood Outlines","County Outlines"),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  addLegend(pal = pal, values = sd$r_COI_met,
            opacity = 0.7, title = NULL,
            position = "bottomright")

```

Column {data-width=300; .tabset}
-----------------------------------------------------------------------

### Poverty

```{r}
fpl_se <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_child_under_fpl,
            x = ~r_SE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children under Federal Poverty Level'),
         xaxis = list(title = 'Social and Economic Index'))

fpl_ed <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_child_under_fpl,
            x = ~r_ED_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children under Federal Poverty Level'),
         xaxis = list(title = 'Education Index'))

fpl_he <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_child_under_fpl,
            x = ~r_HE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children under Federal Poverty Level'),
         xaxis = list(title = 'Health and Invironment Index'))

subplot(fpl_se, fpl_ed,fpl_he, nrows = 3)%>%
  layout(showlegend = FALSE,
         xaxis = list(
           zerolinecolor = '#ffff'
           )
         ) %>%
  plotly_build()
```

### Race

```{r}
race_se <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_nonwhite,
            x = ~r_SE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children who are Non-white'),
         xaxis = list(title = 'Social and Economic Index'))

race_ed <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_nonwhite,
            x = ~r_ED_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children who are Non-white'),
         xaxis = list(title = 'Education Index'))

race_he <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_nonwhite,
            x = ~r_HE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Children who are Non-white'),
         xaxis = list(title = 'Health and Invironment Index'))

subplot(race_se, race_ed, race_he, nrows = 3)%>%
  layout(showlegend = FALSE,
         xaxis = list(
           zerolinecolor = '#ffff'
           )
         ) %>%
  plotly_build()
```

### Aged 0-17

```{r}
ch_se <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_under_18,
            x = ~r_SE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Population Under 18'),
         xaxis = list(title = 'Social and Economic Index'))

ch_ed <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_under_18,
            x = ~r_ED_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Population Under 18'),
         xaxis = list(title = 'Education Index'))

ch_he <- plot_ly(data = sd_df, type = "scatter", mode = "markers") %>%
  add_trace(y = ~pct_under_18,
            x = ~r_HE_met,
            text=sd_df$subneighbor,
            name="Census Tract",
            marker=list(color='#005191'),
            hovertemplate="%{text}")%>%
  layout(showlegend = FALSE,
         yaxis = list(title = 'Percent of Population Under 18'),
         xaxis = list(title = 'Health and Invironment Index'))

subplot(ch_se, ch_ed, ch_he, nrows = 3)%>%
  layout(xaxis = list(
           zerolinecolor = '#ffff'
           ),
         showlegend = FALSE
         ) %>%
  plotly_build()

```

Rankings
=======================================================================

The following presents the range in values between tracts for each index and neighborhood.

Almost all of the large ranges are from suburban Jefferson County, often representing cities with multiple neighborhoods, or small towns that have been combined to create a neighborhood.

Once the data is aggregated, This section will contain a ranking dashboard.

### Histograms

```{r}
ggplotly(
opp_ind %>% 
  filter(year==2015) %>% 
  select(geoid, (starts_with("r")&ends_with("met"))) %>% 
  left_join(neighborhood_by_tract) %>% 
  filter(county_fips %in% county_geoids) %>% 
  pivot_longer(cols = starts_with("r_")) %>%
  group_by(state, county, neighbor, subneighbor, name) %>%
  mutate(range=max(value)-min(value)) %>%
  ungroup() %>% 
  ggplot()+
  geom_histogram(aes(x=range), binwidth = 1) +
  facet_wrap(~name, nrow=1)
)
```

### Table

```{r}
opp_ind %>% 
  filter(year==2015) %>% 
  select(geoid, (starts_with("r")&ends_with("met"))) %>% 
  left_join(neighborhood_by_tract) %>% 
  filter(county_fips %in% county_geoids) %>% 
  pivot_longer(cols = starts_with("r_")) %>%
  group_by(state, county, neighbor, subneighbor, name) %>%
  mutate(range=max(value)-min(value)) %>%
  ungroup() %>% 
  arrange(desc(range)) %>% 
  datatable()

```